---
output: html_document
---
Elements Of Data Visualization: Project 1
===
__By Alex Cortez, Adam Hernandex, and Alex Pearce__

__GitHub__: https://github.com/alexpearce92/DV_RProject1.git

In this project, the group familiarizes itself with git, knitr, ggplot, and basic SQL commands to create **interesting** plots of given data. Additionally, we create graphs usings the entire data set via a provided SQL query. 

## We will first create our data frames.

####We load the necessary libraries ...
```{r message=F, warning=F}
library('RCurl')
library('ggplot2')
```

####Then we query the database and generate our data frames
```{r}
source("../01 Data/create_data_frames.R",echo=TRUE)
```


##Now we create "interesting" graphs:

####Here we can see that most customers hail from California. How delightfully intriguing. 

```{r}
source("../02 Visualizations/interestingplot1.R",echo=TRUE)
```

####And here, It appears some artist price their worth more than others but, no higher than 17 and no less than 13 price units. Quite a fascinating aspect of the data. 

```{r}
source("../02 Visualizations/interestingplot2.R",echo=TRUE)
```

####Here we see that some item ID's have more individual orders (not accounting for quantity of order), than others. Item ID 1 seems to be the hottest commodity! 

```{r}
source("../02 Visualizations/interestingplot3.R",echo=TRUE)
```

####Finally we take a look at the number of orders per month. This was done by some initial data subsetting, followed by a ggplot function. It appears this company does poorly during September and October. Unfortunate. 

```{r}
source("../02 Visualizations/interestingplot4.R",echo=TRUE)
```


##Now to recreate some other interesting graphs using several joins in the creation of our dataframe:

####We first query the database with our SQL statement
```{r}
source("../01 Data/create_joined_data_frames.R",echo=TRUE)
```

####Now let's build some graphs
```{r message=F, warning=F}
source("../02 Visualizations/recreate_plots.R",echo=TRUE)
```