---
output: html_document
---
Elements Of Data Visualization: Project 2, Exoplanet Analysis
===
__By Alex Cortez, Adam Hernandex, and Alex Pearce__

__GitHub__: https://github.com/joseacortez91/DV_RProject2

This project deals with creating interesting graphs of exoplanet data from (**source of the data**), using packages like tidyr and dplyr, as well as our standard class packages.

## Load necessary packages
```{r message=FALSE}
source("../01 Data/load_packages.R",echo=TRUE)
```

## Database Creations
```{r message=FALSE}
source("../01 Data/create-df.R",echo=TRUE)
```

## Data Wrangling

### Isolate mass and radius, grouping the data set into ten percentiles by mass, and generate summary results
```{r message=FALSE}
source("../02 Data Wrangling/mass_radius.R",echo=TRUE)
```

### Plot the curve to show increase in mass and radius at each percentile
```{r message=FALSE, fig.width=12, fig.height=7.5}
source("../03 Visualizations/mass_radius_analysis.R", echo=TRUE)
```

# Orbital Eccentricity Analysis
Via Wikipedia:

> The orbital eccentricity of an astronomical object is a parameter that determines the amount by which its orbit around another body deviates from a perfect circle. A value of 0 is a circular orbit, values between 0 and 1 form an elliptical orbit, 1 is a parabolic escape orbit, and greater than 1 is a hyperbola. The term derives its name from the parameters of conic sections, as every Kepler orbit is a conic section. It is normally used for the isolated two-body problem, but extensions exist for objects following a rosette orbit through the galaxy.

How incredibly interesting. This portion of project 2 deals with analyzing exoplanets of individual solar systems along with their average mass, eccentricity, and orbital period. By using data-wrangling, subsetting the data for this desired visualization was done with ease. We first "zoom-in" to the data by looking at solar systems with more than one planet then "zoom-out" by including all solar-systems. 

##Data Wrangling
```{r message=FALSE}
source("../02 Data Wrangling/eccentricity.R",echo=TRUE)
```

After all null values are filtered out, the SUN column is created by ommiting the last character of the NAMES column in order to provide duplicate values for planets in the same solar system. 

This output is piped for selection of the SUN, ECCENTRICITY, ORB_PERIOD, and MASS columns. 

Subsequent groupby and summarise functions group the planets into their respective suns, and returns the mean of the variables in question. 

Finally, for ease of representing the mean cummulative distribution of planet mass per star, the mass data is piped first with cumme _ dist followed by the ntile function to separate the quantiles of the distribution. 

This Is done yet again for the second graph, yet the filter(Planets >1) workflow portion is ommited. 

##Visualizations
```{r message=FALSE, fig.width=12, fig.height=7.5}
source("../03 Visualizations/eccen_analysis_1.R", echo=TRUE)
```

```{r message=FALSE, fig.width=12, fig.height=7.5}
source("../03 Visualizations/eccen_analysis_2.R", echo=TRUE)
```

There appears to be a pattern in the Mean Orbital Period in regards to Mean Eccentricity, but it's difficult to discern much else without proper statisical analysis and applicable physics knowledge. 

